Global study of well-being and internet adoption | Online analysis supplement

### 2021-11-15 01-clean.Rmd
Add GBD data

# Create directory for intermediate files
dir.create("output", FALSE)
```

@@

The Global Burden of Disease data were downloaded from <http://ghdx.healthdata.org/gbd-results-tool> on 2021-11-02 to `data-raw/GBD/gbd-2021-11-02/`. We selected the relevant locations, age groups, years, and causes from the data tool as detailed in the manuscript. Next we load all tables (inside downloaded `.zip` files, there may be more than one depending on size of downloaded table) inside the directory.

```{r gbd-data-load}
# Load data files and merge to one table
gbd <- list.files(
  "data-raw/GBD/gbd-2021-11-02/", 
  pattern = ".zip", full.names = TRUE, recursive = TRUE
) %>% 
  read_csv()
```

@@

# Merge data tables
gbd <- left_join(gbd, itu)

# Contrast code sex
gbd$sex <- factor(gbd$sex)
contrasts(gbd$sex) <- c(-.5, .5)

# Focus on young people
gbd_all <- gbd
gbd <- gbd %>% 
  filter(age %in% c("15 to 19", "20 to 24"))

# Contrast code binary age in young data set
gbd$age <- factor(gbd$age)
contrasts(gbd$age) <- c(-.5, .5)

# Young data in wide format
gbd_wide <- gbd %>%
  pivot_wider(names_from = cause, values_from = c(val, se))
names(gbd_wide) <- str_remove(names(gbd_wide), "val_")

# Transform edge proportions to fit beta distribution
gbd_10 <- gbd_wide %>% 
  mutate(internet = if_else(internet == 0, .0000000001, internet)) %>% 
  mutate(internet = if_else(internet == 1, .9999999999, internet))
```

We also save a synthetic version of this dataset to better enable others to reproduce our analytical procedures:

@@

>>>>

# Create directory for output files (e.g. plots)
dir.create("output", FALSE)

# Create directory for intermediate data
dir.create("data", FALSE)
```

@@

The Global Burden of Disease data were downloaded from <http://ghdx.healthdata.org/gbd-results-tool> on 2021-11-02 to `data-raw/GBD/`. We include those files in the repository as (permitted by the license](http://ghdx.healthdata.org/):

>"Data made available for download by IHME can be used, shared, modified, or built upon by non-commercial users via the Creative Commons Attribution-NonCommercial-NoDerivatives 4.0 International License. Please refer to our terms and conditions for additional details."

We selected the relevant locations, age groups, years, and causes from the data tool as detailed in the manuscript. Next we load all tables (inside downloaded `.zip` files, there may be more than one depending on size of downloaded table) inside the directory.

```{r gbd-data-load}
# Load data files and merge to one table
gbd <- list.files(
  "data-raw/GBD/", 
  pattern = ".zip", full.names = TRUE, recursive = TRUE
) %>% 
  read_csv()
```

@@

# Merge data tables
gbd <- left_join(gbd, itu)
```

Our primary analysis is about young people but we also look at older groups for supplemental comparison, so we split data here.

```{r}
gbd_all <- gbd
gbd <- gbd %>% 
  filter(age %in% c("10 to 14", "15 to 19", "20 to 24"))
```

We also save a synthetic version of the gwp dataset to better enable others to reproduce our analytical procedures:

@@

```{r}
write_rds(gbd, "data/gbd.rds")
write_rds(gbd_all, "data/gbd_all_ages.rds")
write_rds(itu, "data/itu.rds")
```
